Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-16 ms.tex
added scatter plots showing 217 GHz vs 857 GHz correlation

>>>>

\begin{figure}
\begin{center}
\epsfig{file=scatter_857_217.eps, width=3.3in}
\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
GHz. Left: before correcting for offset and residual Solar dipole. Right: after
correcting or the best-fit offset and dipole amplitude, as described in 
$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
between 857 GHz and 217 GHz.}
\end{center}
\end{figure}
